Higgs Assisted Razor Search for Higgsinos at a 100 TeV $pp$ Collider

### 2019-12-17 main.tex
Clarified differing train-test splits for signal and BG, added note about not using NLO generation mode, added tree depth and node size info

We simulated parton-level events using \texttt{MadGraph5 v2.3.2.2} and
\texttt{MadEvent} \cite{Alwall:2014hca}, then passed those events to Pythia 6
\cite{Sjostrand:2006za} for showering and hadronization. Finally, we used
\texttt{Delphes 3} \cite{deFavereau:2013fsa} to perform a fast, parametrized
detector simulation, with the detector card devised by the FCC-hh working
group\footnote{\url{https://github.com/HEP-FCC/FCCSW/blob/master/Sim/SimDelphesInterface/data/FCChh_DelphesCard_Baseline_v01.tcl}}.
For the backgrounds, we allowed up to one additional jet in the final state, to
approximate NLO QCD effects, and performed MLM matching with the \texttt{xqcut}
parameter set to 40 GeV. The Higgsino pair production cross sections were
calculated using \texttt{Prospino2}~\cite{Beenakker:1999xh} at NLO.  
To decouple the Wino, we set its mass parameter $M_2$ to 3 TeV.

@@

Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
signal benchmark point with $\mu =$ 1 TeV and $M_1$ = 25 GeV.   The
cross-sections of the backgrounds are obtained from MadEvent after performing
the MLM matching procedure. Their small size reflects the $m_{\ell\ell}$ and
$\slashed{E}_T$ cuts we imposed at the parton level. For all the benchmark
points, we require a minimum of three background events (at the MC level, i.e.
unweighted) left over after cuts\footnote{\ap{This is inspired by the upper
    one-sided limit for the mean of a Poisson variable given zero observed
    events, for a confidence level of 95\% (see Table 39.3 of
    \cite{PhysRevD.98.030001}), however, it does not reflect it exactly (since
    we required a minimum on unweighted rather than weighted events).  We
    observed that as we generated more unweighted background events, the
    discovery reach of our analysis showed a steady increase. This, combined
    with the fact that we were pushing the limits of our storage and computing
    capacity (we generated $\approx 10$ million $tt$ events, $\approx 26$
    million $tbW$  events and $100$K $bbWW$ events - all unweighted), lead us
    to believe that the projected reaches presented in this paper are
conservative ones. The ratio of the cross section of the generated events to
that expected at a 100 TeV $pp$ collider with 3 ab$^{-1}$ is $\approx 0.2$ for
$tt$, 0.05 for $tbW$, $0.46$ for $bbWW$}}. We can see that, after applying our
cuts, $tbW$ remains as the dominant backgrounds, followed by $tt$.  The values
of the razor variable cuts were chosen to maximize the significance,
$S/\sqrt{B}$ (calculated for an integrated luminosity of 3000 fb$^{-1}$), shown
in the last column.

@@

For each signal mass combination and each background process, we preselected
events that passed the lepton trigger, contained two SFOS leptons and two
$b$-tagged jets, and calculated a number of kinematic variables for each event.   We then
placed these kinematic variables in an array, with each row corresponding to an
event, and the columns corresponding to the kinematic variables. A mixture of
low-level and high-level kinematic variables was shown to have the greatest
effectiveness. The kinematic variables chosen were $m_{\ell\ell}$, $m_{bb}$,
$M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic transverse energy $H_T$,
and the transverse momenta of individual final state leptons and $b$-quarks:
$p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We then divided
the generated events into training and test sets, with the training set
comprising 75\% of signal events and 30\% of background events.  \Shufang{More details here -- Referee comment 9.} We used the
\texttt{scikit-learn} package  \cite{Pedregosa2011} to implement our analysis.
A boosted decision tree classifier was trained with 1000 weak learners and a
learning rate of 0.025.

@@

\st{For certain values of the
cuts on kinematic variables or the score of the classifier, no events survived
for one or more of the background components. To guard against overly optimistic
estimates of the significance $S/\sqrt{B}$, we set a lower bound of 3 for the
number of Monte Carlo (MC) events after cuts for each background component, corresponding to
the 95\% confidence interval for a Poisson distribution.}\Shufang{SS: Is it 3
MC events, or 3 weighted events after CS values used? Referee comment 10.}
\Adarsh{I added a footnote about this - see footnote 5. I think we can remove
this paragraph...}

>>>>

We simulated parton-level events using \texttt{MadGraph5 v2.3.2.2} and
\texttt{MadEvent} \cite{Alwall:2014hca}, then passed those events to Pythia 6
\cite{Sjostrand:2006za} for showering and hadronization. Finally, we used
\texttt{Delphes 3} \cite{deFavereau:2013fsa} to perform a fast, parametrized
detector simulation, with the detector card devised by the FCC-hh working
group\footnote{\url{https://github.com/HEP-FCC/FCCSW/blob/master/Sim/SimDelphesInterface/data/FCChh_DelphesCard_Baseline_v01.tcl}}.
For the backgrounds, we allowed up to one additional jet in the final state, to
approximate NLO QCD effects, and performed MLM matching\footnote{\ap{Although
there are tools that support NLO generation \cite{Alwall:2014hca}, their NLO
generation mode does not support specifying decay chains, which we require in
order to generate enough MC events to be statistically representative of the
backgrounds at a 100 TeV $pp$ collider.}} with the \texttt{xqcut}
parameter set to 40 GeV. The Higgsino pair production cross sections were
calculated using \texttt{Prospino2}~\cite{Beenakker:1999xh} at NLO.  
To decouple the Wino, we set its mass parameter $M_2$ to 3 TeV.

@@

Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
signal benchmark point with $\mu =$ 1 TeV and $M_1$ = 25 GeV.   The
cross-sections of the backgrounds are obtained from MadEvent after performing
the MLM matching procedure. Their small size reflects the $m_{\ell\ell}$ and
$\slashed{E}_T$ cuts we imposed at the parton level. For all the benchmark
points, we require a minimum of three background events (at the MC level, i.e.
unweighted) left over after cuts\footnote{\ap{This is inspired by the upper
    one-sided limit for the mean of a Poisson variable given zero observed
    events, for a confidence level of 95\% (see Table 39.3 of
    \cite{PhysRevD.98.030001}), however, it does not reflect it exactly (since
    we required a minimum on unweighted rather than weighted events).  We
    observed that as we generated more unweighted background events, the
    discovery reach of our analysis showed a steady increase. This, combined
    with the fact that we were pushing the limits of our storage and computing
    capacity (we generated $\approx 10$ million $tt$ events, $\approx 26$
    million $tbW$  events and $100$K $bbWW$ events - all unweighted), lead us
    to believe that the projected reaches presented in this paper are
conservative ones. The ratio of the cross section of the generated events to
that expected at a 100 TeV $pp$ collider with 3 ab$^{-1}$ is $\approx 0.2$ for
$tt$, 0.05 for $tbW$, and $\approx0.46$ for $bbWW$.}}. We can see that, after applying our
cuts, $tbW$ remains as the dominant backgrounds, followed by $tt$.  The values
of the razor variable cuts were chosen to maximize the significance,
$S/\sqrt{B}$ (calculated for an integrated luminosity of 3000 fb$^{-1}$), shown
in the last column.

@@

For each signal mass combination and each background process, we preselected
events that passed the lepton trigger, contained two SFOS leptons and two
$b$-tagged jets, and calculated a number of kinematic variables for each event.   We then
placed these kinematic variables in an array, with each row corresponding to an
event, and the columns corresponding to the kinematic variables. A mixture of
low-level and high-level kinematic variables was shown to have the greatest
effectiveness. The kinematic variables chosen were $m_{\ell\ell}$, $m_{bb}$,
$M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic transverse energy $H_T$,
and the transverse momenta of individual final state leptons and $b$-quarks:
$p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We then divided
the generated events into training and test sets, with the training set
\ap{comprised of 75\% of the generated signal events and 30\% of the generated
background events. We require a lower portion of the background events for
training, in order to maintain adequate MC statistics to calculate significance
using the testing split, given the extremely large background cross sections at
a 100 TeV $pp$ collider. All the events are unweighted.}
\Shufang{More details here -- Referee comment 9.} We used the
\texttt{scikit-learn} package  \cite{Pedregosa2011} to implement our analysis.
A boosted decision tree classifier was trained with 1000 weak learners and a
learning rate of 0.025. \ap{The maximum tree depth is 3, and the minimum node
size is 1.}

@@

\st{For certain values of the
cuts on kinematic variables or the score of the classifier, no events survived
for one or more of the background components. To guard against overly optimistic
estimates of the significance $S/\sqrt{B}$, we set a lower bound of 3 for the
number of Monte Carlo (MC) events after cuts for each background component, corresponding to
the 95\% confidence interval for a Poisson distribution.}\Shufang{SS: Is it 3
MC events, or 3 weighted events after CS values used? Referee comment 10.}
\Adarsh{I added a footnote about this - see footnote 6 on page 8. I think we can remove
this paragraph...}
